A Search for Supernova Remnants in NGC\,6946

### 2018-11-06 ms.tex
Beginnings of a discussion

\section{Discussion}
Here are some figures we may wish to show, and points we may want to discuss (note: KSL has done some of these figures on Evernote; those all show \oiii-selected objects, which we may choose to omit):
\begin{enumerate}
    \item Correlation between flux from spectra vs imaging (M83 paper, fig 5)
    \item \sii:\ha\ ratio vs \ha\ flux; \sii:\ha\ ratio vs GC distance (fig for this already here)
    \item We don't give any diameter values for objects.  WIYN data are not great for this, but may be worth something.  Also, aren't there WFC3 Pa$\beta$(?) images; are these useful for getting diameters? There are also a handful of \ha\ images (from ACS or WFC2) which should be useful.  If we are to use these, we need to add another short subsection under Observations.
    \item \hb:\ha\ ratio vs GC Distance: done in Evernote; this indicates that reddening is severe throughout \gal, and is most severe near the center.  Happily, this has little effect on the relative strengths of the most interesting lines: \oi, \ha, \nii, and \sii.
    \item Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8)
    \item Comparison to shock models (see existing figure).  This appears to indicate abundances between that of LMC and that of the Galaxy (?)
    \item Also compare these same ratios with other galaxies? (M83 paper, Fig 10)
    \item Separate discussion of historical SNe.  SN1980K and SN2004et are both detected, and both show broad lines.  We see NO evidence for nebular  emission from the other historical SN sites.  See Fig.~\ref{historical_SNe}.
    \item Comparison to MF97
    \item Comparison to Lacey and X-rays catalog and Bruuseman
\end{enumerate}

>>>>

\section{Analysis and Discussion}

We identified 147 candidate SNRs from the WYIN interference images; of these we obtained spectra of 102. The spectra were needed to improve our confidence that the [SII]:\ha\ ratios of the emission nebulae were indeed high and to begin to characterize the SNRs.  The spectroscopic ratios are shown as a function of galactocentric radious in Fig.\ \ref{fig_s2_ha}.  Conventionally, emission nebulae are identified as SNRs optically, if the [SII]:\ha\ ratio exceeds 0.4; 89 of the 102 SNRs with spectra satisfy this criterion, and so we regard these as confirmed SNRs (and they have been listed as such in Table \ref{table_candidates}. Clearly, even though a dividing line of 0.4 is somewhat arbitrary, the other objects should be judged we more suspicion. There are 45 objects without a spectra, so which of these are actually SNRs is uncertain.

\todo[inline]{Find out how many of the MF objects are confirmed.  Make a plote of the imaging and spectroscopic ratios}

Here are some figures we may wish to show, and points we may want to discuss (note: KSL has done some of these figures on Evernote; those all show \oiii-selected objects, which we may choose to omit):
\begin{enumerate}
    \item Correlation between flux from spectra vs imaging (M83 paper, fig 5)
    \item \sii:\ha\ ratio vs \ha\ flux; \sii:\ha\ ratio vs GC distance (fig for this already here)  Check M83 to see if there is a correlation in the spectroscopic ratio with GC, and if so comment on this
    \item We don't give any diameter values for objects.  WIYN data are not great for this, but may be worth something.  Also, aren't there WFC3 Pa$\beta$(?) images; are these useful for getting diameters? There are also a handful of \ha\ images (from ACS or WFC2) which should be useful.  If we are to use these, we need to add another short subsection under Observations.
    \item \hb:\ha\ ratio vs GC Distance: done in Evernote; this indicates that reddening is severe throughout \gal, and is most severe near the center.  Happily, this has little effect on the relative strengths of the most interesting lines: \oi, \ha, \nii, and \sii.
    \item Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8)
    \item Comparison to shock models (see existing figure).  This appears to indicate abundances between that of LMC and that of the Galaxy (?)
    \item Also compare these same ratios with other galaxies? (M83 paper, Fig 10)
    \item Separate discussion of historical SNe.  SN1980K and SN2004et are both detected, and both show broad lines.  We see NO evidence for nebular  emission from the other historical SN sites.  See Fig.~\ref{historical_SNe}.
    \item Comparison to MF97
    \item Comparison to Lacey and X-rays catalog and Bruuseman
\end{enumerate}
